\Huge{Complex State Management with Immutability}

### 2022-03-18 paper.tex
Acknowledgements not necessery

\title{\Huge{Complex State Management with Immutability}}
\author{Nassouh AlOlabi} 
\affil{Scientific supervisor: Dr.Yasser Rahal}
\affil{General supervisor: Dr.Kadan Joumaa} 
\affil{Linguistic supervisor: Fahmi Alammareen}
\setlength{\affilsep}{1pt}
\date{}

@@

\subsection{Structural Sharing}
While imperative programmers are very careful with passing references around and often times rely on cloning. on the other hand persistent data structures allows for more flexibility and safety in sharing and reusing data with ease.
\begin{figure}[H]
    \begin{center}
        {\includegraphics[scale=.65]{originalTree.png}}
    \end{center}
    \caption{ \label{figure:1} Original BST for the corresponding values [a,b,c,d,f,g,h]}
\end{figure}
now what if you wanted to add Node(e) to our Binary Search Tree. now if we were to naively implement an algorithm that would insert the node without mutation is to clone the tree and afterwards do the desired mutations. on the other hand if we consider immutability as and advantage we'll take into account that unaffected node (nodes that we don't need to modify e.g. nodes b,a,c,h) would never change and we can safely reuse them.
\begin{figure}[H]
    \begin{center}
        {\includegraphics[scale=.6]{structuralSharing.png}}
       \end{center}
       \caption{ \label{figure:2} Resulting BST ys which shares most of the elements in xs}
\end{figure}
Structural Sharing is a very powerful technique and is the core concept for many of optimization techniques such as Copy-on-write paging strategies for address space
inheritance have been shown to be effective in reducing the
real time required to perform UNIX fork() operations. This reduction in copying also reduces the amount of
swap space required, reduces the amount of time spent swapping, increases the number of processes which can be run
without paging, and decreases the cost of context switches.[6]

@@

\newpage
\section{Acknowledgements}
Thank you for your time

\printbibliography

>>>>

\title{\Huge{Complex State Management with Immutability}}
\author{Nassouh AlOlabi} 
\affil{Scientific supervisor: Dr.Yasser Rahal}
\affil{General supervisor: Dr.Kadan Joumaa} 
\affil{Linguistic supervisor: Fahmi Al Ammareen}
\setlength{\affilsep}{1pt}
\date{}

@@

\subsection{Structural Sharing}
While imperative programmers are very careful with passing references around and often times rely on cloning. on the other hand persistent data structures allows for more flexibility and safety in sharing and reusing data with ease.
\begin{figure}[H]
    \begin{center}
        {\includegraphics[scale=.65]{originalTree.png}}
    \end{center}
    \caption{ \label{figure:1} Original BST for the corresponding values [a,b,c,d,f,g,h]}
\end{figure}
now what if you wanted to add Node(e) to our Binary Search Tree. now if we were to naively implement an algorithm that would insert the node without mutation is to clone the tree and afterwards do the desired mutations. on the other hand if we consider immutability as and advantage we'll take into account that unaffected nodes (nodes that we don't need to modify e.g. nodes b,a,c,h) would never change and we can safely reuse them.
\begin{figure}[H]
    \begin{center}
        {\includegraphics[scale=.6]{structuralSharing.png}}
       \end{center}
       \caption{ \label{figure:2} Resulting BST ys which shares most of the elements in xs}
\end{figure}
Structural Sharing is a very powerful technique and is the core concept for many of optimization techniques such as Copy-on-write paging strategies for address space
inheritance which have been shown to be effective in reducing the
real time required to perform UNIX fork() operations. This reduction in copying also reduces the amount of
swap space required, reduces the amount of time spent swapping, increases the number of processes which can be run
without paging, and decreases the cost of context switches.[6]

@@
